Group 9 Presentation

### 2021-12-08 presentation.Rmd
Final Changes

paste("The overall fraction of correct predictions in the test dataset is :",(confm2[1,1]+confm2[2,2])/sum(confm2))

@@

ggplot(VI)+geom_col(aes(x=var,y=Overall,fill=var))+coord_flip()+guides(fill=FALSE)+
  labs(x="Variable Name",y="Importance")
```

@@

paste("the overall fraction of correct predictions in the test dataset is :",(confm2[1,1]+confm2[2,2])/sum(confm2))

@@

- Confusion Matrix for Radial:

@@

```{r}
library(knitr)
df1 = data.frame(Method = c("Logistic Regression","LDA","KNN","LASSO","Bagging","Random Forest","Boosting","SVM"),  Overall_Correct_Pred.= c(overall_logit,overall_LDA,overall_knn_1,overall_lasso,overall_bag,overall_RF,overall_boost,overall_SVM))

>>>>

paste("Accuracy :",(confm2[1,1]+confm2[2,2])/sum(confm2))

@@

ggplot(VI)+geom_col(aes(x=var,y=Overall,fill=var))+coord_flip()+guides(fill="none")+
  labs(x="Variable Name",y="Importance")
```

@@

paste("Accuracy :",(confm2[1,1]+confm2[2,2])/sum(confm2))

@@

- Confusion Matrix for Radial Kernel:

@@

```{r}
library(knitr)
df1 = data.frame(Method = c("Logistic Regression","LDA","KNN","LASSO","Bagging","Random Forest","Boosting","SVM"),  Accuracy= c(overall_logit,overall_LDA,overall_knn_1,overall_lasso,overall_bag,overall_RF,overall_boost,overall_SVM))
